Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-12 paper/paper.tex
compressing the analysis in appendix

      \sum_{n \geq 0} \tfrac{

@@

In \eqref{eq:ard-kl-div-real} we need $

@@

$:
\begin{align}

@@

    &= \frac12 e^{- \tfrac\lambda2}
    \int_0^\infty \sum_{n \geq 0} \biggl(
        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
        \tfrac{e^{- \tfrac{x}2}}{\Gamma(n + \tfrac{m}2)}
        \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
    \biggr) \log{(x)} dx

@@

    &= e^{- \tfrac\lambda2} \sum_{n \geq 0}
        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
    \tfrac1{\Gamma(n + \tfrac{m}2)}

@@

        (\log2 + \log u) du

@@

    &= \log{2}

@@

        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}

@@

@@

    = \frac{d}{dx} \log \Gamma(x)

@@

% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
% $. By the ratio test, the dominating
% series has infinite radius:
% $$
% \lim_{n\to\infty}
%   \biggl\lvert
%     \frac{
%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
%     }{
%       x^n \log{(n + \tfrac{m}2)} (n+1)!
%     }
%   \biggr\rvert
%   = \lim_{n\to\infty}
%     \lvert x \rvert 
%     \biggl\lvert
%       \frac{
%         \log{(n + 1 + \tfrac{m}2)}
%       }{
%         \log{(n + \tfrac{m}2)} (n+1)
%       }
%     \biggr\rvert
%   % = \lim_{n\to\infty}
%   %   \lvert x \rvert 
%   %   \biggl\lvert
%   %     \frac{
%   %       n + \tfrac{m}2
%   %     }{
%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
%   %     }
%   %   \biggr\rvert
%   = 0 < 1
%   \,, $$
% since
% $$
% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
%   \sim \frac{\log{(x+1)}}{x \log{x}}
%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
%   \to 0
%   \,. $$
% A theorem from calculus states, that the formal series derivative (integral)
% coincides with the derivative (integral) of the function, corresponding to
% the power series (everywhere on the convergence region). And the convergence
% regions of derivative (integral) coincide with the region of the original
% power series.

Differentiating the series within $g_m$ yields
\begin{equation}  \label{eq:g-m-deriv}
  \frac{d}{d x} g_m(x)
    % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
    %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
    % )
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
    = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
    \,.
\end{equation}
Since $
    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
$ on $\mathbb{R}$, for $\alpha\neq 0$ we have
% $
%   \int_0^x t^{\alpha-1} dt
%     = \tfrac{x^\alpha}{\alpha}
% $ and
\begin{equation}  \label{eq:g-m-deriv-int-1}
  \sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
    % = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
    = \int_0^x t^{\alpha-1} e^t dt
    \,,
  % the MCT ([0, x], \mathcal{B}([0, x]), dx)
\end{equation}
by the monotone convergence theorem, whence
\begin{equation}  \label{eq:g-m-deriv-int-2}
  \eqref{eq:g-m-deriv}
    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
    %     \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
    % = x^{-\tfrac{m}2} e^{-x}
    %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
    = x^{-\tfrac{m}2} e^{-x}
        \int_0^x t^{\tfrac{m}2 - 1} e^t dt
    \,.
\end{equation}
The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
\begin{equation}  \label{eq:g-m-deriv-int-3}
  \frac{d}{d x} g_m(x)
    % = x^{-\tfrac{m}2} e^{-x}
    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
    = 2 x^{-\tfrac{m}2} e^{-x}
        \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
    \,.
\end{equation}
In particular, for $m=1$ we get
\begin{equation}  \label{eq:g-m-series-one}
  g_1(x)
    = - \gamma - 2 \log{2}
    + e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \sum_{p=1}^n \frac2{2p - 1}
    \,,
\end{equation}
and the derivative \eqref{eq:g-m-deriv} can be computed thus
\begin{equation}  \label{eq:g-m-deriv-one}
  \frac{d}{d x} g_1(x)
    = 2 \tfrac{F(\sqrt{x})}{\sqrt{x}}
    \,,
\end{equation}
using $
  F \colon \mathbb{R} \to \mathbb{R}
  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
$ Dawson's integral (special function).

@@

% essential intro into Wirtinger calculus (CR)
% https://math.stackexchange.com/a/444493
Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
  \real \times \real
$, and regards $
  f\colon \cplx \to \cplx
$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
  f(z) = f(u + jv) = F(u, v)
$. Within this framework the differential of $f$ at $z \in \cplx$ is
$$
df(z) \big\vert_{z=u + jv}
  = \frac{\partial f}{\partial z} dz
    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
   % = \frac12\bigl(
   %    \frac{\partial}{\partial u}
   %    - j \frac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % + \frac12\bigl(
   %    \frac{\partial}{\partial u}
   %    + j \frac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % = \frac12 \bigl(
   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
   % \bigr)
   % + \frac12 \bigl(
   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
   % \bigr)
   = \frac{\partial F}{\partial u} du
     + \frac{\partial F}{\partial v} dv
   = dF(u, v)
  \,, $$
with formally defined derivatives $
  \tfrac{\partial}{\partial z}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      - j \tfrac{\partial}{\partial v}
    \bigr)
$ and $
  \tfrac{\partial}{\partial \conj{z}}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      + j \tfrac{\partial}{\partial v}
    \bigr)
$, and differentials $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the
complex argument and its conjugate are treated as independent variables. Cauchy-Riemann
conditions $
  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
$ scan be expressed as $
  \tfrac{\partial f}{\partial \conj{z}} = 0
$ in this notation. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus on
holomorphic functions, when $f(z)$, regarded as $f(z, \conj{z})$, is constant with respect
to $\conj{z}$. The usual rules of calculus, like chain and product rules, follow directly
from the definition of the operators, e.g.
$$
  \frac{\partial (f\circ g)}{\partial z}
    = \frac{\partial f(g(z))}{\partial g} \frac{\partial g(z)}{\partial z}
    + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g(z)}}{\partial z}
    % = \nabla G \nabla F
  \,. $$
% Show that $dh(z) = df(g(z)) dg(z)$.
% $h(z) = f(g(z)) = F(G_r(u, v), G_i(u, v)) = H(u, v)$
% $$
% dH
%   = \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial u} du
%   + \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial v} dv
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial u} du
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial v} dv
%   = \tfrac{\partial F}{\partial r} d\Re g(z)
%   + \tfrac{\partial F}{\partial i} d\Im g(z)
%   = df(\Re g(z) + j\Im g(z)) d g(z)
%   = df(g(z)) d g(z)
%   \,. $$

>>>>

      \sum_{n \geq 0} \frac{

@@

The expectation $

@@

$, needed in \eqref{eq:ard-kl-div-real}, by integrating power series \eqref{eq:nonchisq-density}
with substitution $x \to 2u$ equals
\begin{multline}  \label{eq:exp-log-chisq-proof}

@@

    % &\frac12 e^{- \tfrac\lambda2}
    % \int_0^\infty \sum_{n \geq 0} \biggl(
    %     \frac{
    %       e^{- \tfrac{x}2} \bigl(\tfrac\lambda2\bigr)^n
    %     \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
    % \biggr) \log{(x)} dx

@@

    e^{- \tfrac\lambda2} \sum_{n \geq 0}
        \frac{\bigl(\tfrac\lambda2\bigr)^n}{

@@

        \log{(2 u)} du

@@

    % \notag
    \\
    = \log{2}

@@

        \frac{\bigl(\tfrac\lambda2\bigr)^n}{n!}

@@

\end{multline}

@@

    % = \frac{d}{dx} \log \Gamma(x)

@@

% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
% $. By the ratio test, the dominating
% series has infinite radius:
% \lim_{n\to\infty}
%   \biggl\lvert
%     \frac{
%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
%       x^n \log{(n + \tfrac{m}2)} (n+1)!
%   \biggr\rvert
%   = \lim_{n\to\infty}
%     \lvert x \rvert 
%     \biggl\lvert
%       \frac{
%         \log{(n + 1 + \tfrac{m}2)}
%         \log{(n + \tfrac{m}2)} (n+1)
%     \biggr\rvert
%   % = \lim_{n\to\infty}
%   %   \lvert x \rvert 
%   %   \biggl\lvert
%   %     \frac{
%   %       n + \tfrac{m}2
%   %     }{
%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
%   %     }
%   %   \biggr\rvert
%   = 0 < 1
%   \,, $$
% since
% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
%   \sim \frac{\log{(x+1)}}{x \log{x}}
%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
%   \to 0
% A theorem from calculus states, that the formal series derivative (integral)
% coincides with the derivative (integral) of the function, corresponding to
% the power series (everywhere on the convergence region). And the convergence
% regions of derivative (integral) coincide with the region of the original
% power series.
Differentiating the power series within $g_m$ yields
\begin{equation}  \label{eq:g-m-deriv}
  \frac{d}{d x} g_m(x)
    % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
    %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
    % )
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
From $
    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
$ on $\mathbb{R}$ and $
  \tfrac{x^\alpha}{\alpha}
    = \int_0^x t^{\alpha-1} dt
$ for $\alpha\neq 0$ we get
\begin{equation}  \label{eq:g-m-deriv-int-1}
  \sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
    % = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
    = \int_0^x t^{\alpha-1} e^t dt
  % the MCT ([0, x], \mathcal{B}([0, x]), dx)
by the monotone convergence theorem, whence
\begin{equation}  \label{eq:g-m-deriv-int-2}
  \eqref{eq:g-m-deriv}
    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
    %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
        \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
    % = x^{-\tfrac{m}2} e^{-x}
    %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
    = x^{-\tfrac{m}2} e^{-x}
        \int_0^x t^{\tfrac{m}2 - 1} e^t dt
The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
\begin{equation}  \label{eq:g-m-deriv-int-3}
  \frac{d}{d x} g_m(x)
    % = x^{-\tfrac{m}2} e^{-x}
    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
    = 2 x^{-\tfrac{m}2} e^{-x}
        \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
In particular, for $m=1$ we get
\begin{equation}  \label{eq:g-m-series-one}
  g_1(x)
    = - \gamma - 2 \log{2}
    + e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \sum_{p=1}^n \frac2{2p - 1}
and the derivative \eqref{eq:g-m-deriv} can be computed thus
\begin{equation}  \label{eq:g-m-deriv-one}
  \frac{d}{d x} g_1(x)
    = 2 \tfrac{F(\sqrt{x})}{\sqrt{x}}
using $
  F \colon \mathbb{R} \to \mathbb{R}
  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
$ Dawson's integral (special function).

@@

% essential intro into Wirtinger calculus (CR)
% https://math.stackexchange.com/a/444493
Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
  \real \times \real
$, and regards $
  f\colon \cplx \to \cplx
$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
  f(z) = f(u + jv) = F(u, v)
$. Within this framework the differential of $f$ at $z = u + jv \in \cplx$ is
$$
df(z)
  = \frac{\partial f}{\partial z} dz
    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
   % = \frac12\bigl(
   %    \frac{\partial}{\partial u}
   %    - j \frac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % + \frac12\bigl(
   %    \frac{\partial}{\partial u}
   %    + j \frac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % = \frac12 \bigl(
   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
   % \bigr)
   % + \frac12 \bigl(
   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
   % \bigr)
   = \frac{\partial F}{\partial u} du
     + \frac{\partial F}{\partial v} dv
   = dF(u, v)
  \,, $$
with formally defined derivatives $
  \tfrac{\partial}{\partial z}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      - j \tfrac{\partial}{\partial v}
    \bigr)
$ and $
  \tfrac{\partial}{\partial \conj{z}}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      + j \tfrac{\partial}{\partial v}
    \bigr)
$, and differentials $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the
complex argument and its conjugate are treated as independent variables. Cauchy-Riemann
conditions $
  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
$ scan be expressed as $
  \tfrac{\partial f}{\partial \conj{z}} = 0
$ in this notation. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus on
holomorphic functions, when $f(z)$, regarded as $f(z, \conj{z})$, is constant with respect
to $\conj{z}$. The usual rules of calculus, like chain and product rules, follow directly
from the definition of the operators, e.g.
$$
  \frac{\partial (f\circ g)}{\partial z}
    = \frac{\partial f(g(z))}{\partial g} \frac{\partial g(z)}{\partial z}
    + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g(z)}}{\partial z}
    % = \nabla G \nabla F
  \,. $$
% Show that $dh(z) = df(g(z)) dg(z)$.
% $h(z) = f(g(z)) = F(G_r(u, v), G_i(u, v)) = H(u, v)$
% $$
% dH
%   = \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial u} du
%   + \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial v} dv
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial u} du
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial v} dv
%   = \tfrac{\partial F}{\partial r} d\Re g(z)
%   + \tfrac{\partial F}{\partial i} d\Im g(z)
%   = df(\Re g(z) + j\Im g(z)) d g(z)
%   = df(g(z)) d g(z)
%   \,. $$
